Clines from PDE

### 2015-10-23 notes/pde-clines.Rmd
changed r

Let's solve this numerically.
```{r solve_pde_setup, cache=TRUE}
s <- 0.1
tau <- 100
thegrid <- setup.grid.1D(x.up=-15, x.down=15, N = 5000)
cline.A <- setup.prop.1D(grid=thegrid, func=tanh_cline, s=s)
cline.B <- setup.prop.1D(grid=thegrid, func=function(x,s)1-tanh_cline(x,s), s=s)
yinit <- c( rep(1.0,thegrid$N), rep(0.0,thegrid$N) )
tt <- seq(0,tau,length.out=100)
r <- 1
pde.fn <- function (t,y,parms,...) {
    yA <- y[1:thegrid$N]
    yB <- y[thegrid$N+(1:thegrid$N)]
    tran.A <- tran.1D(C=yA, A=cline.A, D=1/2, dx=thegrid)$dC
    tran.B <- tran.1D(C=yB, A=cline.B, D=1/2, dx=thegrid)$dC
    list( c( 
            tran.A + r * cline.B$mid * (yB-yA),
            tran.B + r * cline.A$mid * (yA-yB)
            ) )
}
pde.soln <- ode.1D( y=yinit, times=tt, func=pde.fn, nspec=2 ) # note FIRST COLUMN IS TIME
image(pde.soln,legend=TRUE,main=sprintf("q for z=%s, r=%0.3f",c("A","B"),r), yaxt='n', ylab='space',zlim=c(0,1))
axis(2,at=(pretty(thegrid$x.mid)-min(thegrid$x.mid))/diff(range(thegrid$x.mid)),labels=pretty(thegrid$x.mid))
```
These combine to give the predicted cline:
```{r show_pde_cline,cache=TRUE,depends="solve_pde_setup"}
A.inds <- 1+(1:thegrid$N)
B.inds <- 1+thegrid$N+(1:thegrid$N)
pde.cline <- cbind( pde.soln[,1], pde.soln[,A.inds]*cline.A$mid[col(pde.soln[,A.inds])] + pde.soln[,B.inds]*cline.B$mid[col(pde.soln[,B.inds])] )
attributes(pde.cline) <- c( attributes(pde.cline), attributes(pde.soln)[setdiff(names(attributes(pde.soln)),c("dim","dimnames"))] )
attr(pde.cline,"nspec")<-1
image(pde.cline,legend=TRUE,zlim=c(0,1),main=sprintf("clines, at r=%0.2f",r))
# same thing, plotted with lines
clineplot(pde.cline,main=sprintf("clines, at r=%0.2f",r))
```

>>>>

Let's solve this numerically.
```{r solve_pde_setup, cache=TRUE}
s <- 0.1
tau <- 100
thegrid <- setup.grid.1D(x.up=-15, x.down=15, N = 5000)
cline.A <- setup.prop.1D(grid=thegrid, func=tanh_cline, s=s)
cline.B <- setup.prop.1D(grid=thegrid, func=function(x,s)1-tanh_cline(x,s), s=s)
yinit <- c( rep(1.0,thegrid$N), rep(0.0,thegrid$N) )
tt <- seq(0,tau,length.out=100)
r <- 0.1
pde.fn <- function (t,y,parms,...) {
    yA <- y[1:thegrid$N]
    yB <- y[thegrid$N+(1:thegrid$N)]
    tran.A <- tran.1D(C=yA, A=cline.A, D=1/2, dx=thegrid)$dC
    tran.B <- tran.1D(C=yB, A=cline.B, D=1/2, dx=thegrid)$dC
    list( c( 
            tran.A + r * cline.B$mid * (yB-yA),
            tran.B + r * cline.A$mid * (yA-yB)
            ) )
}
pde.soln <- ode.1D( y=yinit, times=tt, func=pde.fn, nspec=2 ) # note FIRST COLUMN IS TIME
image(pde.soln,legend=TRUE,main=sprintf("q for z=%s, r=%0.3f",c("A","B"),r), yaxt='n', ylab='space',zlim=c(0,1))
axis(2,at=(pretty(thegrid$x.mid)-min(thegrid$x.mid))/diff(range(thegrid$x.mid)),labels=pretty(thegrid$x.mid))
```
These combine to give the predicted cline:
```{r show_pde_cline,cache=TRUE,depends="solve_pde_setup"}
A.inds <- 1+(1:thegrid$N)
B.inds <- 1+thegrid$N+(1:thegrid$N)
pde.cline <- cbind( pde.soln[,1], pde.soln[,A.inds]*cline.A$mid[col(pde.soln[,A.inds])] + pde.soln[,B.inds]*cline.B$mid[col(pde.soln[,B.inds])] )
attributes(pde.cline) <- c( attributes(pde.cline), attributes(pde.soln)[setdiff(names(attributes(pde.soln)),c("dim","dimnames"))] )
attr(pde.cline,"nspec")<-1
image(pde.cline,legend=TRUE,zlim=c(0,1),main=sprintf("clines, at r=%0.2f",r))
# same thing, plotted with lines
clineplot(pde.cline,main=sprintf("clines, at r=%0.2f",r))
```
